---
title: 'Gerontology & Aging: A Data Science Perspective'
author: "Bryan Victor"
date: "Thursday, January 08, 2015"
output: word_document
---

The following data are drawn from those journals in the fields of gerontology & aging that are currently indexed by psycINFO.  Data from all available articles (n= 47,281) published in the following journals were included:

Activities, Adaptation & Aging
Ageing & Society
Aging & Mental Health
Aging, Neuropsychology, and Cognition
The American Journal of Geriatric Psychiatry
Archives of Gerontology and Geriatrics
Australasian Journal on Ageing
Canadian Journal on Aging
Clinical Gerontologist: The Journal of Aging and Mental Health
Dementia and Geriatric Cognitive Disorders
Drugs & Aging
Educational Gerontology
European Journal of Ageing
Experimental Aging Research
Frontiers in Aging Neuroscience
Geriatrics & Gerontology International
Gerontechnology
The Gerontologist
Gerontology
Gerontology & Geriatrics Education
GeroPsych: The Journal of Gerontopsychology and Geriatric Psychiatry
The International Journal of Aging & Human Development
International Journal of Geriatric Psychiatry
Journal of Aging and Health
Journal of Aging and Physical Activity
Journal of Aging Studies
Journal of Applied Gerontology
Journal of Cross-Cultural Gerontology
Journal of Elder Abuse & Neglect
Journal of Geriatric Psychiatry and Neurology
Journal of Gerontological Social Work
Journal of Nutrition in Gerontology and Geriatrics
Journal of Religion, Spirituality & Aging
Journal of the American Geriatrics Society
Journal of Women & Aging
The Journals of Gerontology: Series A: Biological Sciences and Medical Sciences
The Journals of Gerontology: Series B: Psychological Sciences and Social Sciences
Neurobiology of Aging
Physical & Occupational Therapy in Geriatrics
Psychology and Aging
Research on Aging
Reviews in Clinical Gerontology
Revista Española de Geriatrí?a y Gerontologí?a
Tijdschrift voor Gerontologie en Geriatrie
Zeitschrift für Gerontologie und Geriatrie

```{r, echo=FALSE, comment=NA}

setwd("C:/Users/Tom/Documents/GitHub/AgingDataScience")

AgingWrangle<-read.csv("FINAL_AgingWrangle.csv")

library(dplyr)
library(stringr)
library(ggplot2)

```


# Which journals have published the most number of articles since being established?

```{r, echo=FALSE, comment=NA}
n.so.yr <- filter(AgingWrangle, attributes == "SO" | attributes == "YR")

n.so <- filter(AgingWrangle, attributes == "SO") %>% mutate(title = record) %>% 
        select(-attributes, -record)

n.yr <- filter(AgingWrangle, attributes == "YR") %>% mutate(year = record ) %>% 
        select(-attributes, -record)

n.yr$year<-as.character(n.yr$year)
n.yr$year<-as.numeric(n.yr$year)

n.so.yr <- left_join(n.so, n.yr) %>%
    group_by(title) %>%
    summarise(first = min(year), last = max(year), n.to.date = n()) %>%
    arrange(desc(n.to.date))

# 10 highest number of publications
head(n.so.yr, 10)

```



```{r, echo=FALSE}

```


